---
title: "Trabajo con mapas"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introducción
En este documento trabajaremos para explorar la identidad de plantas de *tacsonia* del Perú

## trabajando con los datos
Vamos a cargar las librerias
```{r}
library(tidyverse)
```

Ahora voy a leer los datos
```{r}
library(readr)
plants <- read_csv("Datos.csv", locale=locale(encoding="latin1"))
```

Ahora voy a hacer el código que voy a ejecutar. Exploraremos la base de datos
```{r}
huamachucoensis <- plants %>% 
  dplyr::filter(ESPECIES == "P. huamachucoensis L.K. Escobar")
nueva <- plants %>% 
  dplyr::filter(ESPECIES == "P. nueva")
amazonica <- plants %>% 
  dplyr::filter(ESPECIES == "P. amazonica L. K. Escobar")
anastomosans <- plants %>% 
  dplyr::filter(ESPECIES == "P. anastomosans (Lamb. Ex Dc.) Killip")
cumbalensis <- plants %>% 
  dplyr::filter(ESPECIES == "P. cumbalensis (H. Karst.) Harms")
glaberrima <- plants %>% 
  dplyr::filter(ESPECIES == "P. glaberrima (Juss.) Poir")
gracilens <- plants %>% 
  dplyr::filter(ESPECIES == "P. gracilens (A. Gray) Harms")
kuethiana <- plants %>% 
  dplyr::filter(ESPECIES == "P. kuethiana B. Esquerre")
lanceolata <- plants %>% 
  dplyr::filter(ESPECIES == "P. lanceolata (Mast.) Harms")
mandonii <- plants %>% 
  dplyr::filter(ESPECIES == "P. mandonii (Mast.) Killip")
manicata <- plants %>% 
  dplyr::filter(ESPECIES == "P. manicata (Juss.) Pers.")
mathewsii <- plants %>% 
  dplyr::filter(ESPECIES == "P. mathewsii (Mast.) Killip")
mixta <- plants %>% 
  dplyr::filter(ESPECIES == "P. mixta L.f.")
parvifolia <- plants %>% 
  dplyr::filter(ESPECIES == "P. parvifolia (DC.) Harms")
pedunculatis <- plants %>% 
  dplyr::filter(ESPECIES == "P. peduncularis Cav.")
pinnatistipula <- plants %>% 
  dplyr::filter(ESPECIES == "P. pinnatistipula Cav.")
runa <- plants %>% 
  dplyr::filter(ESPECIES == "P. runa L. K Escobar")
salpoense <- plants %>% 
  dplyr::filter(ESPECIES == "P. salpoense S. Leiva & Tantalean")
tarminiana <- plants %>% 
  dplyr::filter(ESPECIES == "P. tarminiana Coppens y V. E. Barney")
trifoliata <- plants %>% 
  dplyr::filter(ESPECIES == "P. trifoliata Cav.")
tripartita <- plants %>% 
  dplyr::filter(ESPECIES == "P. tripartita (Juss.) Poir.")
trisecta <- plants %>% 
  dplyr::filter(ESPECIES == "P. trisecta Mast.")
weberbaueri <- plants %>% 
  dplyr::filter(ESPECIES == "P. weberbaueri Harms")
weigendii <- plants %>% 
  dplyr::filter(ESPECIES == "P. weigendii T. Ulmer & Schwerdtferger")
xrosea <- plants %>% 
  dplyr::filter(ESPECIES == "P. x rosea (H. Karst.) Killip")
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
