---
title: "Trabajo con mapas"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introducción
En este documento trabajaremos para explorar la identidad de plantas de *tacsonia* del Perú

## trabajando con los datos
Vamos a cargar las librerias
```{r}
library(tidyverse)
```

Ahora voy a leer los datos
```{r}
library(readr)
plants <- read_csv("Datos.csv", locale=locale(encoding="latin1"))
```


## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
